Carrying out Latent Profile Analysis in Accordance With Best Practices: A Tutorial Using the tidyLPA R package

### 2020-02-04 paper.rmd
update

``` {r, eval = FALSE, curry-mac-mplus}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, package = "MplusAutomation")
```

@@

``` {r, eval = F}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, 
                    variances = "varying",
                    covariances = "varying")
```

@@

``` {r, compare-mclust, eval = FALSE}
curry_mac_solutions <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))

3Best model according to AIC is Model 6 with 7 classes.
# Best model according to BIC is Model 6 with 2 classes.

@@

@@

``` {r, compare-mplus, eval = TRUE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9, package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))

@@

```{r}

```

>>>>

``` {r, curry-mac-mplus, eval = FALSE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, package = "MplusAutomation")
```

@@

``` {r, curry-mac-m6, eval = F}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(3, 
                    variances = "varying",
                    covariances = "varying")
```

@@

``` {r, compare-mclust, eval = FALSE}
curry_mac_mclust_solutions <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))

write_rds(curry_mac_mclust_solutions, "cm_mclust.rds")

# Best model according to AIC is Model 6 with 7 classes.
# Best model according to BIC is Model 6 with 2 classes.

@@

````{r, just-one}
curry_mac_mclust_j <- curry_mac %>% 
  select(KinshipR:PossessionR) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))

write_rds(curry_mac_mclust_j, "cm_mclust_r.rds")

curry_mac_mclust_j <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))

write_rds(curry_mac_mclust_j, "cm_mclust_j.rds")

curry_mac_mclust_j <- curry_mac %>% 
  select(KinshipR:PossessionR) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9,
                    package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))

write_rds(curry_mac_mclust_j, "cm_mclust_r.rds")

curry_mac_mclust_j <- curry_mac %>% 
  select(KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9,
                    package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))

write_rds(curry_mac_mclust_j, "cm_mclust_j.rds")
```

@@

``` {r, compare-mplus, eval = TRUE}
curry_mac_mplus_solutions <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9, package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))

write_rds(curry_mac_mplus_solutions, "cm_mplus.rds")

@@

```{r, m6ps-mplus, error = TRUE}
curry_mac_m6p2_mplus <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(n_profiles = 2, 
                    variances = "varying",
                    covariances = "varying", 
                    package = "mplus")

# equivalent to model 6

plot_profiles(curry_mac_m6p2_mplus)
```

```{r, m6p2-mclust}
curry_mac_m6p2 <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(n_profiles = 2, 
                    variances = "varying",
                    covariances = "varying")

plot_profiles(curry_mac_m6p2)
```

### 2020-02-04 paper.tex
update

\includegraphics{paper_files/figure-latex/unnamed-chunk-8-1.pdf}

@@

@@

@@

\begin{verbatim}
## # A tibble: 700 x 9
##    model_number classes_number broad_interest enjoyment self_efficacy Class
##           <dbl>          <int>          <dbl>     <dbl>         <dbl> <dbl>
##  1            1              3            3.8       4            1        1
##  2            1              3            3         3            2.75     3
##  3            1              3            1.8       2.8          3.38     3
##  4            1              3            1.4       1            2.75     2
##  5            1              3            1.8       2.2          2        3
##  6            1              3            1.6       1.6          1.88     3
##  7            1              3            3         3.8          2.25     1
##  8            1              3            2.6       2.2          2        3
##  9            1              3            1         2.8          2.62     3
## 10            1              3            2.2       2            1.75     3
## # … with 690 more rows, and 3 more variables: Class_prob <int>,
## #   Probability <dbl>, id <int>
\end{verbatim}

@@

\hypertarget{htmlwidget-a6cf205f9fe062a59d12}{}

>>>>

\includegraphics{paper_files/figure-latex/curry_mac_p3-1.pdf}

\begin{verbatim}
## Warning: Using shapes for an ordinal variable is not advised
\end{verbatim}

\includegraphics{paper_files/figure-latex/curry_mac_p3-2.pdf}

@@

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_3_class_3, model_3_class_6, model_3_class_8

## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_3_class_3, model_3_class_6, model_3_class_8
\end{verbatim}

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_5, model_1_class_6, model_1_class_8, model_1_class_9, model_2_class_6, model_2_class_7, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_6_class_1, model_6_class_2, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9

## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_5, model_1_class_6, model_1_class_8, model_1_class_9, model_2_class_6, model_2_class_7, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_6_class_1, model_6_class_2, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9
\end{verbatim}

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_6, model_1_class_7, model_1_class_8, model_1_class_9, model_2_class_5, model_2_class_6, model_2_class_7, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_6_class_1, model_6_class_2, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9

## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_6, model_1_class_7, model_1_class_8, model_1_class_9, model_2_class_5, model_2_class_6, model_2_class_7, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_6_class_1, model_6_class_2, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9
\end{verbatim}

The results of this analysis suggests that the Model 6, two or seven class models are best.

\includegraphics{paper_files/figure-latex/m6p7-solution-1.pdf}

\includegraphics{paper_files/figure-latex/m6p2-solution-1.pdf}

@@

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_5, model_1_class_6, model_1_class_7, model_1_class_8, model_1_class_9, model_2_class_5, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_6_class_1, model_6_class_2, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9

## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_1_class_5, model_1_class_6, model_1_class_7, model_1_class_8, model_1_class_9, model_2_class_5, model_2_class_8, model_2_class_9, model_3_class_1, model_3_class_2, model_3_class_3, model_3_class_4, model_3_class_5, model_3_class_6, model_3_class_7, model_3_class_8, model_3_class_9, model_6_class_1, model_6_class_2, model_6_class_3, model_6_class_4, model_6_class_5, model_6_class_6, model_6_class_7, model_6_class_8, model_6_class_9
\end{verbatim}

\begin{verbatim}
## Warning: 
## One or more analyses resulted in warnings! Examine these analyses carefully: model_6_class_2
\end{verbatim}

\begin{verbatim}
## Error in plot_profiles.default(x = list(df_plot = structure(list(Class = structure(c(1L, : Could not match raw data to model estimates.
\end{verbatim}

\includegraphics{paper_files/figure-latex/m6p2-mclust-1.pdf}

@@

\begin{verbatim}
## # A tibble: 700 x 9
##    model_number classes_number broad_interest enjoyment self_efficacy Class
##           <dbl>          <int>          <dbl>     <dbl>         <dbl> <dbl>
##  1            1              3            3.8       4            1        1
##  2            1              3            3         3            2.75     3
##  3            1              3            1.8       2.8          3.38     2
##  4            1              3            1.4       1            2.75     2
##  5            1              3            1.8       2.2          2        2
##  6            1              3            1.6       1.6          1.88     2
##  7            1              3            3         3.8          2.25     3
##  8            1              3            2.6       2.2          2        3
##  9            1              3            1         2.8          2.62     2
## 10            1              3            2.2       2            1.75     2
## # … with 690 more rows, and 3 more variables: Class_prob <int>,
## #   Probability <dbl>, id <int>
\end{verbatim}

@@

\hypertarget{htmlwidget-5db543d8ea5b00cc330c}{}
